\mytitle

### 2015-07-25 MSc_diss.tex
Minor changes in description of the chemical mechanism

The constructed chemical mechanism has a limited representation of organic chemistry. It includes (oxidation schemes)/(degradation reactions) of only seven alkanes: methane ($CH_4$), ethane ($C_2H_6$), propane ($C_3H_8$), n-butane ($nC_4H_{10}$), i-butane ($iC_4H_{10}$), n-pentane ($nC_5H_{12}$) and i-pentane ($iC_5H_{12}$). While the oxidation scheme of $CH_4$ is full, oxidation of other six alkanes is not full, but terminated at different oxidation steps.

It has been done due to computational restrictions and  because otherwise the mechanism would 
Another limitation of the model's chemical mechanism is that it does not consider all possible organic reactions (which otherwise could lead to a too large number of reactions but is focused on representing the oxidation of alkanes
full oxidation scheme for methane ($CH_4$) only .

@@

@@

>>>>

The constructed chemical mechanism has a limited representation of organic chemistry. It includes oxidation of only seven alkanes: methane ($CH_4$), ethane ($C_2H_6$), propane ($C_3H_8$), n-butane ($nC_4H_{10}$), i-butane ($iC_4H_{10}$), n-pentane ($nC_5H_{12}$) and i-pentane ($iC_5H_{12}$). $CH_4$ undergoes a full oxidation in the model, but oxidation of other six alkanes follows the reaction sequence:
\begin{itemize}
\item[] $RH + OH \rightarrow RO_2 + H_2O$
\item[] $RO_2 + HO_2 \rightarrow ROOH + O2$
\item[] $RO_2 + NO \rightarrow RO + NO_2$
\item[] $ROOH + hv \rightarrow RO + OH$
\item[] $ROOH + OH \rightarrow products$
\item[] $RO + O_2 \rightarrow products$
\end{itemize}
and is 'terminated' at different oxidation steps. Ethane oxidation is terminated after the formation of the acetylperoxyl radicals ($C_2H_3CO_3$), propane - after the formation of the propyldioxy radicals ($C_3H_5O_3$), n-butane - after the formation of ethanal ($CH_3CHO$), butanal ($C_3H_7CHO$), methyl ethyl ketone ($C_2H_5COCH_3$), and 1-($\lambda^1$-oxidanylmethoxy)-2-methoxy-ethane ($C_4H_9O_3$), i-butane - after the formation of 2-methylpropanal ($iso-C_3H_7CHO$) and acetone ($CH_3COCH_3$), n-pentane - after the formation of pentanal ($C_4H_9CHO$), methyl propyl ketone ($n-C_3H_7COCH_3$), and diethyl ketone ($(C_2H_5)_2CO$), i-pentane - after the formation of 2-methylbutanal ($sec-C_4H_9CHO$) and isopropyl methyl ketone ($iso-C_3H_7COCH_3$). It has been done to limit the number of reactions in the mechanism, which otherwise would include 1678 reactions describing evolution of 539 species, and therefore would be computationally too expensive. For the same reason all self-reactions of organic peroxy radicals ($RO_2$) are omitted as well. To avoid a huge impact of incomplete oxidation of alkanes on the results the model's simulation time has been restricted to 24 hours.

No halon chemistry.

@@

\begin{figure}[h]
\includegraphics[width=0.5\linewidth]{{./pics/Sillman1999_Fig1}.png}
%\caption{chem_allAN_netO3_rate}
\label{fig:O3observations}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3_rate.png}
%\caption{chem_allAN_netO3_rate}
\label{fig:O3observations}
\end{figure}
